Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-04-07 src/tex/ms.tex
Modify Table 3

\begin{table}
    \caption{
        Comparison of our constraints to \citet{Okounkova_2022} and \citet{Wang_2021}.
        The constraint from \citet{Okounkova_2022} is given at 68\% credibility, while the other two are given at 90\% credibility.
        The constraint on $M_{PV}$ is a lower limit, while the constraint on $\tilde{\kappa}$ and $\kappa$ is an upper limit.
    }
    \begin{ruledtabular}
        \variable{output/comparison_summary.txt}
    \end{ruledtabular}
    \label{tab:comparison_summary}
\end{table}

>>>>

\begin{table}
    \caption{
        Comparison of our constraints to \citet{Okounkova_2022} and \citet{Wang_2021}.
        CL is the percentage of the one-sided credible limit of each work.
    }
    \begin{ruledtabular}
        \variable{output/comparison_summary.txt}
    \end{ruledtabular}
    \label{tab:comparison_summary}
\end{table}
